\problemname{Stand Behind Braum!}

Braum is a tank character in the Multiplayer Online Battle Arena game League of Legends. Braum’s task is to absorb as
much damage from the enemy so that his allies may win the fight. Recently, Braum's performance has fallen off and he just isn't as
dominant as he once was. Refusing to be upset, Braum instead decides to hunker down and figure out some strategies so that he can 
be a better tank. He decides that if he can calculate the amount of incoming damage, he can adjust his item purchases to
better protect his allies.\\

Given an incoming onslaught of attacks, Braum wants to calculate the Total Damage he’ll take.
Attacks come in three damage types, \textbf{Physical Damage}, \textbf{Magical Damage}, and \textbf{True Damage}.
We can calculate the Total Damage Taken as a sum of the Physical, Magical, and True Damage Taken:

\begin{align*}
    \text{Physical Damage Taken} &= \text{Physical Damage} \cdot \left( \frac{100}{100 + \text{Armor}}\right) \\
    \text{Magical Damage Taken} &= \text{Magical Damage} \cdot \left( \frac{100}{100 + \text{MR}}\right) \\
    \text{True Damage Taken} &= \text{True Damage}
\end{align*}

Braum notices that the total damage posseses the following relationship, $\alpha + \beta + \tau = 1$ . And furthermore
where the values of $\alpha, \beta, \tau$ possess the following relationships:
\begin{align*}
    \alpha &= \frac{\text{Physical Damage}}{\text{Total Damage}} \\
    \beta &= \frac{\text{Magical Damage}}{\text{Total Damage}} \\
    \tau  &= \frac{\text{True Damage}}{\text{Total Damage}}\\
\end{align*}

\section*{Input}
You will be given two lines of input. The first line contains $\alpha$, $\beta$, $\tau$, and $x$ representing the
percent of Physical, Magical, True, and Total damage. The second line contains the Armor and MR values that Braum has.

\section*{Output}
Output the Total Damage Taken by Braum from the incoming attacks, rounded down to the nearest integer value.
