\problemname{Silent Mist}
\illustration{.4}{fog}{\href{https://pixabay.com/p-594286/?no_redirect}{pixabay}, CC0}



\noindent After a long and ardous journey you and your convoy, have finally entered the the Mist Dragon's domain,
Niebla. Upon entering the Niebla's domain you notice a dangerous mist engulf the area and your units immediately lose
some health. The members all turn to you for answers, and in desperation you look around and notice a royal knight
slumped on one of the trees nearby. \\

\noindent As you approach the knight you notice that they must have passed away from from the exposure to the mist, how
unforuntate. In their hand they hold a letter with the king's seal. You fetch the letter from the knightus cold hands,
and begin reading it: \\

\begin{minipage}[t]{6in}
To my Royal Guard, \\

By the time you will have opened this letter you will have reached Niebla's domain, a truly dreadful place. As you may
have already noticed, the mist poses a hazard to your health. Your health points will be drained, on certain
\textbf{dangerous} paths, and you will suffer damage equal to the time need to cross. I have managed to get our
country's best wizards to conjure a potion which will make you temporarily invulnerable when passing through a dangerous
path. Unfortunately this potion is in limited reserves, so use it wisely. \\

We will provide you a map on the back of this letter outlining the safe points within the mist, and the relative danger
of the mist between these safe points, collected over several of our past expeditions in this domain.\\

Best,\\
The King \\
\end{minipage}



\noindent With this information in hand, you would like to determine if possible,  the shortest time required to get
through the Niebla's domain, with the mist's constraints on your health. \\

\section*{Input}

\noindent The first line of input will consist of three integers $N, M, T, P$
( $2 \leq N, H \leq 5000$, $ 1 \leq M \leq N^2$, $1 \leq P \leq 10$), representing the the number of safe spots, the
number of paths, the amount of time your convoy can withstand in dangerous mist before they perish, and the amount of
uses the king's potion(s) will allow. \\

\noindent Following this will be $M$ lines composed of four integers describing the information of a path:
$u_i~ v_i, t_i, m_i$ \\ ($1 \leq u_i,v_i \leq S$ and $1 \leq t_i, m_i \leq 10000$), representing the starting safe point,
the ending safe point, the time required to traverse this path, and 1 if this path is dangerous, 0 otherwise; this path
is bidrectional. Following this will be two integers $S$, the safe spot you begin your journey
from and, $E$, the last safe spot this is outside of Niebla's domain. \\

\section*{Output}

Your output should consist of one integer, being the minimum amount of time required to get your convoy from $S$ to
$E$. if this is impossible then print the phrase "retreat".
