\problemname{Ore mines}
\illustration{.5}{anvil}{Wikimedia, cc-by-sa}

\noindent You have been contacted by your convoy's blacksmith, he informs you that he's running out of ore and would like
some assitance in gather the resources required for your future journeys.\\

\noindent Just like your own world, ore is quite difficult to obtain in this world.  First, you must determine
a number of safe mining pits; for which your workers will begin mining from. Then you must determine the density
of the rockbead on the paths in between these mining pits. In this world there are three types of rocks:
\textbf{softrock}, \textbf{hardrock} and \textbf{superhardrock}. superhardrock is impossible to mine through and should
be ignored, and hardrock is more difficult to mine through than softrock so you would like minimize
the number of hardrock patches you mine through, softrock is the most optimal choice.\\ \\

\noindent Currently the only way to access your mining pits is to walk above ground and enter the mining pit from above.
This time around you would like to to connect all of your mining pits, so it will be easier to traverse them underground
on future expeditions. Your objective on this expedition is to maximize the ore mined on your expedition but above all
else you will also want to minimize the number of hardrock paths you must choose. You may assume that there is always a
way to connect the nodes, and that any paths between nodes not specified are superhardrock.


\section*{Input}
Input will consit of $1 \leq N \leq 100$, the number of mining pits, $1 \leq M \leq 10000$, the number of possible paths
between your mining pits. Following this will be $M$ lines, each with four integers $a,b,c,d$. Each line signifies a
possible (bidirectonal) link between mining pit a and b, with cost c. d will be 1 if the path is hardrock, and 0
otherwise.

\section*{Output}
Your output should be two integers, one specifying the minimum amount of hardrock paths required to connect these mines,
and two being the amount of ore mined on this expedition.

